Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-01-05 transmission.tex
Clarify the procedure and justification for inference check

To check the performance of the inference procedure, I calculated the coverage of the 50\%, 75\%, and 95\% central credible intervals for each parameter and simulation.
I define coverage as the proportion of simulations where the true value of the parameter in that simulation was within the credible interval.
This procedure is a simplified version of simulation-based calibration~\autocites{cookValidation}{taltsValidating}.
The coverage for each parameter should equal the nominal probability (\eg the coverage should be 50\% for the 50\% credible intervals).
I constructed a confidence interval for the coverage using the Pearson-Klopper method implemented in the binom package~\autocite{binom1-1}.

>>>>

To check the performance of the inference procedure, I calculated the coverage of the 50\%, 75\%, and 95\% central credible intervals for each parameter and simulation.
Define coverage as the proportion of simulations where the true value of the parameter in that simulation was within the credible interval.
As the parameters are drawn from the prior, if the inference is performed correctly then the coverage for each parameter should equal the nominal probability (\eg the coverage should be 50\% for the 50\% credible intervals)~\autocite{cookValidation}.
This check is related to, although simpler than, simulation-based calibration~\autocite{taltsValidating}.
I constructed a confidence interval for the coverage using the Pearson-Klopper method implemented in the binom package~\autocite{binom1-1}.
